\documentclass[10pt, courier]{navyletter}

\author{S. R. Eastberg}
\title{Letter of promulgation}
\navysubj{Letter of promulgation}
\navyfiling{}
\navyserial{}
\date{\today}
%\navymarking{for training use only}

\navyaddresszero{Department of the Navy}
\navyaddressone{Naval Air Systems Command}
\navyaddresstwo{47123 Buse Road, Bldg 2272}
\navyaddressthree{Patuxend River, MD 20670-1547}

\begin{document}
\makedateblock{}

\begin{navyletterheader}
\navyfrom{Commander, Naval Air Systems Command}
\navysubjline{}%
\end{navyletterheader}

\section{} The Naval Air Training and Operating Procedures Standardization (NATOPS) Program is a positive approach toward improving combat readiness and achieving a substantial reduction in the aircraft mishap rate. Standardization, based on professional knowledge and experience, provides the basis for development of an efficient and sound operational procedure. The standardization program is not planned to stifle individual initiative, but rather to aid the commanding officer in increasing the unit’s combat potential without reducing command prestige or responsibility.

\section{} This manual standardizes ground and flight procedures but does not include tactical doctrine. Compliance with the stipulated manual requirements and procedures is mandatory except as authorized herein. In order to remain effective, NATOPS must be dynamic and stimulate rather than suppress individual thinking. Since aviation is a continuing, progressive profession, it is both desirable and necessary that new ideas and new techniques be expeditiously evaluated and incorporated if proven to be sound. To this end, commanding officers of aviation units are authorized to modify procedures contained herein, in accordance with the waiver provisions established by OPNAVINST 3710.7, for the purpose of assessing new ideas prior to initiating recommendations for permanent changes. This manual is prepared and kept current by the users in order to achieve maximum readiness and safety in the most efficient and economical manner. Should conflict exist between the training and operating procedures found in this manual and those found in other publications, this manual will govern.

\section{} Checklists and other pertinent extracts from this publication necessary to normal operations and training should be made and carried for use in naval aircraft.

%\respectfully{}
\noclosing{}
\signspace{}
\signature{S. R. Eastburg}
\sendertitle{RADM, USN}
\bydirection

\end{document}